ED2 model notes

### 2019-01-31 analysis/paper/ed-notes.Rmd
PAPER: Add description of N limitation to photosynthesis

>>>>

### Calculating N supply and demand for live tissue growth

Basically, N limitation places a limit on the fraction of stomata that are open (due to N limitation; `cpatch%fsn`).

Calculating changes in live biomass (subroutines `dbalive_dt` and `dbalive_dt_eq_0` in `dynamics/growth_balive.f90`).

If plant limitation enabled, call subroutine `potential_N_uptake` to see what would happen if stomata were open.
This sets the value of potential N uptake (`N_uptake_pot`).

If no limitation, set fraction of open stomata (from N limitation; `fsn`) to 1.
Otherwise, calculate N limitation factor.

```
#- dynamics/growth_balive.f90:L293
nitrogen_supply = plant_N_supply_scale * broot * mineralized_soil_N
fsn = nitrogen_supply / (nitrogen_supply + N_uptake_pot)
```

### Initialization from near bare ground

Subroutines `near_bare_ground_init` and `near_barea_ground_big_leaf_init` (in `init/ed_nbg_init.f90`):

If there is N limitation, initialize as follows:

- Fast soil C (`fast_soil_C`): 0.2
- Slow soil C (`slow_soil_C`): 0.01
- Structural soil C (`structural_soil_C`): 10.0
- Structural soil lignin (`structural_soil_L`): 10.0
- Mineralized soil N (`mineralized_soil_N`): 1.0
- Fast soil N (`fast_soil_N`): 1.0

If no N limitation, set all of these to zero.
